The Rapid Cycleway Prioritisation Tool

### 2020-06-15 rapid-slides.Rmd
Add top ranked cycleways slide

>>>>

<!-- ![](figures/results-top-leeds.png) -->

- All road sections with spare lanes or estimated width > 10 m (CyIPT)
- Of those, which have a minum continuous length of at least 500 m?
- Rank the roads by cycling potential (commute + school, Government Target)
- Show the top n, where n depends on the size of the region (70 in London)

![](https://raw.githubusercontent.com/cyipt/popupCycleways/master/figures/results-top-leeds.png)
